The LHC as a Neutrino-Ion Collider

### 2024-01-29 journal_sub/sec-results.tex
revised flux uncertainty discussion

>>>>

\paragraph{The effect of neutrino flux uncertainties.}
%
The results presented so far assume the incoming far-forward neutrino flux as input, with vanishing uncertainties.
%
One can estimate the impact that uncertainties associated to this neutrino flux input have
on the PDF constraints by extending the procedure of~\cite{Kling:2023tgr}, 
based on the predictions provided in~\cite{Ahn:2009wx, Ahn:2011wt, Riehn:2015oba, Fedynitch:2018cbl, Pierog:2013ria, Buonocore:2023kna, Roesler:2000he, Fedynitch:2015kcn, Bai:2020ukz, Bai:2021ira, Bai:2022xad, Ostapchenko:2010vb, Bhattacharya:2023zei, Fieg:2023kld, Maciula:2022lzk},
by introducing an additional fit parameter to account for the overall normalisation of the neutrino flux (while assuming the shape is unchanged with respect to the baseline predictions).
%
The constraint for this flux normalisation parameter is obtained considering two scenarios: first, by using the expected Run 3 data from FASER$\nu$, and second, by using 50\% of the data expected at FASER$\nu$2 during the HL-LHC run.
%
In the latter case, only the remaining 50\% of FASER$\nu$2 data is then considered available for PDF determination, to avoid double counting.

The resulting flux normalisation parameter can be constrained approximately to a precision of
6\% using FASER$\nu$
Run 3 data, and to
0.4\% using 50\% of FASER$\nu$2 data, as illustrated in Fig.~\ref{fig:flux_constraints}.
%
These constraints are then incorporated into
the profiling studies as additional fully correlated (across bins) uncertainties, also accounting for an increase in statistical uncertainty in the case where only 50\% of data is used.
%
The impact on the FASER$\nu$2 projections of the neutrino flux uncertainties, in the case of the 
PDFs resulting from using the Run 3 constraint are shown in Fig.~\ref{fig:FASERv2_flux_unc_run3}, and those obtained with the HL-LHC constraints in Fig.~\ref{fig:FASERv2_flux_unc_HL-LHC}.
%
In either case, the results indicate only a very small increase in the resulting PDF uncertainties.
%
One may conclude that neutrino flux uncertainties do not significantly degrade the PDF constraining potential of the FPF experiments presented in this work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\centering
\includegraphics[width=0.4\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/normalization_constraint_run3.pdf}
\hspace{1cm}
\includegraphics[width=0.4\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/normalization_constraint_HL-LHC.pdf}
\caption{The baseline uncertainty associated to the theoretical modelling of the far-forward muon neutrino fluxes~\cite{Kling:2023tgr} at FASER$\nu$ (left) and FASER$\nu$2 (right panel), compared to the results of constraining the overall normalisation of this flux from  FASER$\nu$ data and from 50\% of the expected FASER$\nu$2 data, respectively. 
}
\label{fig:flux_constraints}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\centering
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/fred05fcorr05_fluxR3_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/fred05fcorr05_fluxR3_FASERv2_q2_10000_pdf_dv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/fred05fcorr05_fluxR3_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/fred05fcorr05_fluxR3_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/fred05fcorr05_fluxR3_FASERv2_q2_10000_pdf_s_ratio.pdf}
\caption{
  Same as Fig.~\ref{fig:FASERnu2_baseline}, now quantifying the
  impact on the FASER$\nu$2 results of accounting for the muon neutrino flux uncertainties, assuming its
  overall normalisation has been constrained with FASER$\nu$ Run 3 data.
  %
  See text for more details.
}
\label{fig:FASERv2_flux_unc_run3}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\centering
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/fred05fcorr05_fluxR4_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/fred05fcorr05_fluxR4_FASERv2_q2_10000_pdf_dv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/fred05fcorr05_fluxR4_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/fred05fcorr05_fluxR4_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/fred05fcorr05_fluxR4_FASERv2_q2_10000_pdf_s_ratio.pdf}
\caption{
  Same as Fig.~\ref{fig:FASERnu2_baseline} now quantifying the
  effect of neutrino flux uncertainties in the analysis of FASER$\nu$2 pseudodata, assuming that the neutrino flux normalisation is constrained using 50\% of FASER$\nu$2 data to constrain the flux and the remainder for PDF determination. 
}
\label{fig:FASERv2_flux_unc_HL-LHC}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
